The pollination trade-off

### 2018-11-24 paper/manuscript.Rmd
make slopes plot wider

# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
rw <- c(9,1.2, 6.5,1.2)

>>>>

# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
width_left <- 6.5*3/5
bar_plot_width <- 0.325
rw <- c(width_left - bar_plot_width,
        bar_plot_width, 
        6.5 - width_left - bar_plot_width,
        bar_plot_width)
